**Evaluation of machine learning methods for 16S rRNA gene data**

### 2019-03-18 submission/manuscript.Rmd
permutation

>>>>

The classification models were built to classify normal versus adenoma, normal versus carcinoma, and high versus low SCFA concentrations. The regression models were built to classify the SCFA concentrations of acetate, butyrate, and propionate regardless of disease status. The featThe bacterial abundances are the features used to predict colonic disease status. Bacterial abundances are discrete data in the form of Operational Taxonomic Unit (OTU) counts. There are 6920 OTUs for each sample. FIT levels are continuous data present for each sample. Because the data are in different scales, features are transformd by scaling each feature to a [0-1] range

To evaluate the model performances, we randomly split the data into training/validation and test sets 100 times with a 80/20 proportion. Data-splits were stratified for diagnosis or SCFA concentration levels in classification models. For each data-split, training/validation set consisted of x patients (x carcinoma, y adenoma, z normal), while the test set was composed of x patients (x carcinoma, y adenoma, z normal). The training/validation data was used for training purposes and validation of hyperparameter selection, and the test set was used for evaluation purposes. Validation of hyperparameter selection was performed by randomly splitting the training/validation set into stratified training and validation sets 100 times with a 80/20 proportion [Figure 1].
